---
title: Emily's Dynamic Report 🪩
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

#🛑 Scientific notations 
options(scipen=999)

```

```{css}

h2 {
padding: 10px; 
background-color:#ffe6ff;
}

body {
  font-family: "Playfair Display", serif;
  font-size: 20 px;
  font-weight: <weight>;
  font-style: normal;
  background-color: #ffffcc
      }
```

## A 'Study' about Study Breaks 🍫

**What is the subject being observed?**

Well, a huge clue is in the heading! This dynamic report tracks the study breaks taken by university students. As a part of the Google form, participants were asked to answer the following questions:

1.  What time of day was the break was taken;
2.  The main reason for taking the break i.e. exhaustion, hunger, routine;
3.  The duration of the study break;
4.  If the participant used an electronic device / did a physical activity / eat or drank during the break; and
5.  How ✨refreshed✨ they felt afterwards.

**Look at me to see some of the responses**

```{r, echo = F}

#importing the data into R & creating a data frame 

form_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vS-4ALIuD7LTPFVJz39UB452ycH7GKS6wy3dkNK_x0hdQb_frktGseG3iuOk_9-MVwaZBYYMmLjKIMp/pub?output=csv"

logged_data <- read_csv(form_url) 

logged_data %>% 
  slice(1:10) %>%
  print()

#renaming the variables & creating a new data frame
latest_data <- logged_data %>%
  rename(time_of_day = 2, 
         study_time = 3, 
         reason = 4, 
         break_duration = 5, 
         device_use = 6, 
         physical_activity = 7,
         food_or_drink = 8, 
         extent_of_refreshment = 9) 
```

`r nrow(logged_data)` participants responded to this survey at this very moment. However, if you come back to it later, something *dynamic* might happen 👀

## What activity will make one feel more refreshed?

Well, let's see below.

```{r, echo=F, fig.width = 5.5, fig.height=4}

  ggplot(latest_data) +
    geom_bar(aes(x = extent_of_refreshment, fill = device_use)) + 
    theme_minimal() + 
    labs(title = "Device use & Extent of Refreshment", 
         subtitle = "From participants of Emily & Mimi's survey")
    
  
  ggplot(latest_data) +
    geom_bar(aes(x = extent_of_refreshment, fill = physical_activity)) + 
    theme_classic() + 
    labs(title = "Physical activity & Extent of Refreshment", 
         subtitle = "From participants of Emily & Mimi's survey")
  
  ggplot(latest_data) +
    geom_bar(aes(x = extent_of_refreshment, fill = food_or_drink)) + 
    theme_get() + 
    labs(title = "Food / Drink consumption & Extent of Refreshment", 
         subtitle = "From participants of Emily & Mimi's survey")
```

## Some dynamic comments

**What are the most popular activities on study break?**

```{r}

device_yes_count <- latest_data %>%
    filter(device_use == "Yes") %>%
    nrow()
  
  device_yes_percentage <- round((device_yes_count / nrow(latest_data)) * 100, 1)

  
paste0("So ",device_yes_percentage, "% of the participants used a device on break.")


 #What % of people did some sort of physical activity? 
  
  activity_yes_count <- latest_data %>%
    filter(physical_activity == "Yes") %>%
    nrow()

  
  activity_yes_percentage <- round((activity_yes_count / nrow(latest_data)) * 100, 1)
  
paste0("And ",activity_yes_percentage, "% of the participants did some kind of physical activity (ie walk, chores).")

 #What % of people had food or drinks?
  food_yes_count <- latest_data %>%
    filter(food_or_drink == "Yes") %>%
    nrow()
  
  activity_yes_percentage <- round((food_yes_count / nrow(latest_data)) * 100, 1)
  
paste0("Last but not least, ",activity_yes_percentage, "% of the participants consumed food / drink.")

```

**You may still be wondering, what activity makes people feel the most refreshed...**

If you want the answer, then I shall provide

```{r, echo = F}
  
  #average feeling of refreshment if someone used devices
  average_device_refreshment_ <- latest_data %>%
    filter(device_use == "Yes") %>%
    summarise(average_device_refreshment_ = mean(extent_of_refreshment, na.rm = TRUE))

  #average feeling of refreshment if physical activity was completed 
  mean_physical_activity_refreshment <- latest_data %>%
    filter(physical_activity == "Yes") %>%
    summarise(mean_physical_activity_refreshment = mean(extent_of_refreshment, na.rm = TRUE))
  
  #average feeling of refreshment if consumed food / drink 
  mean_consumption_refreshment <-  latest_data %>%
    filter(food_or_drink == "Yes") %>%
    summarise(mean_consumption_refreshment = mean(extent_of_refreshment, na.rm = TRUE))
  
  paste0("On average, if people used devices, they feel ",round(average_device_refreshment_, 1), " / 5 refreshed")
  
  
    paste0("On average, if people did physical activities, they feel ",round(mean_physical_activity_refreshment, 1), " / 5 refreshed")
  
      paste0("On average, if people consumed food / drinks, they feel ",round(mean_consumption_refreshment, 1), " / 5 refreshed")
  
    
```

Hope that answers your question :)

And now, it's time to

![](https://lh7-rt.googleusercontent.com/formsz/AN7BsVDZxwgbVTbHWSUshZwXf6BqPrCl_oRbDVy6_HWl0h2d2K-Ag4dT0Vpc7iSvybkh4_75nJniHfix_gfYDXRtwswMindZH9Xq2UaQvCTF7eWgbXHQPbPJHlUy-5L5vkBp80mCUi0x7kcZDfxfQIqn2WGwsigMCLgqoEXCSw?key=D4gF2Y8io-3iVmWvjUziKg)

